---
title: "Analysis and Results"
---

Overall, the first year of the program has been a success, with an overall mean completion rate of 71.5%. The t-test for this outcome indicates that the overall results are significant at p < .001.

```{r}
t.test(NSO_Complete_Code, mu = 0, alternative = "two.sided")
```

## Summary Statistics

### Program Completion Progress
```{r, echo=FALSE}
PSOM_Orientation2$NSO_completion_group <- factor(PSOM_Orientation2$NSO_completion_group,levels = c("0%", "1% to 25%", "26% to 50%", "51% to 75%", "76% to 99%", "100%"))
PSOM_Orientation2 %>% ggplot(aes(x = NSO_completion_group)) + geom_bar() +
        labs(x = "Percent Complete", y = "Count", title = "New Staff Orientation Program", subtitle = "Performance Distribution") + 
        theme_stata() + scale_fill_stata() + scale_color_stata()
```

The analysis of results as measured by how much of the program was completed by particpants shows the breakdowm of performance as:

Outcome       |  n  | Percentage
----------------------------------
Never Started | 117 | 16.0%
Incomplete    |  92 | 12.5%
Complete      | 525 | 71.5%

A closer look at the Incomplete category shows the breakdown progress as:

Outcome       |  n  | Percentage
----------------------------------
1% to 25%     |  33 | 35.9%
26% to 50%    |  41 | 44.6%
51% to 75%    |  12 | 13.0%
76% to 99%    |   6 |  6.5%

### Time to start

```{r}
PSOM_Orientation2 %>% summarize(mean(Days_to_access, na.rm = TRUE))
```

The average number of days between assignment of the program to participants and starting the program was 8.15 days.

```{r}
PSOM_Orientation2 %>% summarize(mean(Days_to_complete, na.rm = TRUE))
```

For those who completed the program, the average time to complete was 17.0 days. This was well within our 30 day expected completion time frame.

## Analysis of Variables

### Summary of Categorical Explanatory Variables
A logistic regression analysis on the identified explanatory variables shows the following results:

```{r}
summary(glm(NSO_Complete_Code ~ factor(Emp_age_group) + 
                    factor(Emp_Gender) + factor(Exempt_Status) + 
                    factor(Salary_Code) + factor(Personnel_Class) + 
                    factor(SUP_Employee_Type) +
                    factor(SUP_Learning), family = "binomial", data = PSOM_Orientation2))
```

The results of this test indicate the only coefficient with significant results was for Employees ages 25 to 34. A plot of the means with confidence intervals helps to see the source of this effect.

```{r}

PSOM_Orientation2 %>% ggplot(aes(Emp_age_group, NSO_Complete_Code)) + 
        stat_summary(fun.y = mean, geom = "point", size = 3) + 
        stat_summary(fun.data = mean_se, geom = "errorbar") +
        labs( x = "Age", y = "NSO Complete", 
        title = "New Staff Orientation Program - Age Group vs. Completion", 
        subtitle = "Error Bar using mean as center with Confidence Intervals") +
        theme_stata() + scale_color_stata()
```


This means that we are able to say that the odds of an employee 18-25 years old completing the orientation program was XX% lower than that of an employee 25 to 34 years old.

### Summary of explanatory continuous variables

If the program variables, *Days_to_complete* and *Days_to_access* are treated as continuous variables, we can plot them to see if any relationship is present.

```{r}
ggplot(PSOM_Orientation3, aes(x = Days_to_access, y = Days_to_complete)) + 
        geom_point() + geom_smooth(method=lm, se=FALSE, fullrange=TRUE) +
        labs( x = "Days to Access", y = "Days to Complete", 
        title = "New Staff Orientation Program", subtitle = "Days to Access vs. Days to Complete") + 
        scale_fill_stata(name = "Status") +
        theme_stata() + scale_color_stata()

```

This plot indicates a positive, linear relationship which is confirmed by running a regression analysis.

```{r}
summary(lm(Days_to_complete ~ Days_to_access, PSOM_Orientation3))
```

Finally, we can test the hypothesis that the length of time between when the program is associated with the likelihood of completion.

```{r}
summary(glm(NSO_Complete_Code ~ Days_to_access), family = "binomial")
```

